\documentclass[master=ewit,english]{kulemt}
\setup{title={Building a state of the art speech recogniser},
  author={Moritz Wolter},
  promotor={Prof.\,dr.\,ir.\ Patrick Wambacq },
  assessor={Prof.\,dr.\,ir.\ Johan Suykens},
  assistant={Ir. Vincent Renkens}}
% The following \setup may be removed entirely if no filing card is wanted
\setup{filingcard,
  translatedtitle=,
  udc=621.3,
  shortabstract={
  	In the past machine learning relied heavily on algorithms designed by experts to solve a specific task. Which lead to highly sophisticated algorithms, which could be grasped only by small groups of people. The human brain however does not work this way, although specialized areas exist, these areas consist of similar
  	building blocks. Artificial neural networks attempt to mimic this layout. Similar algorithmic structures are used for a wide variety of tasks. This thesis deals with\ the application of neural networks in speech recognition.  Replacing the various	subsystems by one integrated network based approach.   
    \endgraf}}
% Uncomment the next line for generating the cover page
%\setup{coverpageonly}
% Uncomment the next \setup to generate only the first pages (e.g., if you
% are a Word user.
%\setup{frontpagesonly}

% Choose the main text font (e.g., Latin Modern)
\setup{font=lm}

% If you want to include other LaTeX packages, do it here. 
\input{preamble.tex}

% Finally the hyperref package is used for pdf files.
% This can be commented out for printed versions.
\usepackage[pdfusetitle,colorlinks,plainpages=false,hidelinks]{hyperref}


\begin{document}


\begin{preface}
  I would like to thank everybody who kept me busy the last year,
  especially my promotor and my assistants. I would also like to thank the
  jury for reading the text. My sincere gratitude also goes to my family
  for supporting me trough my studies.
\end{preface}

\tableofcontents*

\begin{abstract}
  The \texttt{abstract} environment contains a more extensive overview of
  the work. But it should be limited to one page.

\end{abstract}

% A list of figures and tables is optional
%\listoffigures
%\listoftables
% If you only have a few figures and tables you can use the following instead
\listoffiguresandtables
% The list of symbols is also optional.
% This list must be created manually, e.g., as follows:
\chapter{List of Abbreviations and Symbols}
\section*{Abbreviations}
\begin{flushleft}
  \renewcommand{\arraystretch}{1.1}
  \begin{tabularx}{\textwidth}{@{}p{12mm}X@{}}
    ConvNet   & Convolutional neural network \\
    MSE   & Mean Square error \\
    PSNR  & Peak Signal-to-Noise ratio \\
  \end{tabularx}
\end{flushleft}
\section*{Symbols}
\begin{flushleft}
  \renewcommand{\arraystretch}{1.1}
  \begin{tabularx}{\textwidth}{@{}p{12mm}X@{}}
    42    & ``The Answer to the Ultimate Question of Life, the Universe,
            and Everything'' according to \cite{h2g2} \\
    $c$   & Speed of light \\
    $E$   & Energy \\
    $m$   & Mass \\
    $\pi$ & The number pi \\
  \end{tabularx}
\end{flushleft}

% Now comes the main text
\mainmatter

\import{../chapters/}{intro}
%\import{../chapters/}{chap-1}
%\import{../chapters/}{chap-2}
% ... and so on until
%\import{../chapters/}{chap-n}
%\import{../chapters/}{conclusion}

% If you have appendices:
%\appendixpage*          % if wanted
%\appendix
%\include{app-A}
% ... and so on until
%\include{app-n}

\backmatter
% The bibliography comes after the appendices.
% You can replace the standard "abbrv" bibliography style by another one.
\bibliographystyle{abbrv}
\bibliography{../chapters/references}

\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
